---
title: "Analysing times series with riscoBrasil"
author: "Robert Myles McDonnell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysing times series with riscoBrasil}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The 'Brazil Risk' numbers, [published daily](http://www.ipeadata.gov.br/ExibeSerie.aspx?serid=40940&module=M) by the [Brazilian Institute of Geography and Statistics](http://www.ibge.gov.br/english/) from JP Morgan's [Emerging Market Bond Index](https://en.wikipedia.org/wiki/JPMorgan_EMBI), are a time-series spanning 1994 to the present, and as such, are a great source of data to use for the teaching of time series in R.

## Forecasting with riscoBrasil


```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
